### 2023-08-28 main.tex
Fix 4

@@

@@

Formula \eqref{W-extended} comes from standard perturbation theory. However, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system. This expression, as it will be show in the following sections, allows to find explicit expression of the eigenvector by the Bethe ansatz and also allows to retrieve again the steady state of $H^{''}$ by applying $W$ to the ground state. To find it, we use the Quantum Inverse Scattering Method (QISM). We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$. 

@@

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
\begin{equation}
		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

Since $Q^{2L}$ and $H$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with this more with this expression. Hopefully, using exchange relation between charges, we could try to handle \eqref{WInCharges} and rewrite it independently from the equilibrium eigenvectors. Moreover, we can use it to extract the steady state by rising the vacum state. 

@@

Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and making it act on 

@@

We use the following power expansion

@@

@@

Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains. Repeating the computations we find that 

@@

 Recalling the expression of $\mathcal{Q}^{2L}$ given in \eqref{Q-nonDiag} we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$. We obtain that, using the multi-variate version of \eqref{veryUsefulSeries},

@@

Here $SYM$ is the following transformation. Introduce, the following $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$ indices, such that 

@@

@@

&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\&:=\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}

@@

\subsection{Eigenvectors of the non equilibrium Hamiltonian}
For simplicity we first consider the case with $N=3$. We make the following ansatz for the eigenvectors of the chain with left triangular and right diagonal boundaries described by the Hamiltonian $H^{''}$ introduced in \eqref{HSecond}. We denote by $\Delta_{2}=\alpha_{2}-\beta_{2}$ and $\Delta_{3}=\alpha_{3}-\beta_{3}$. The eigenvectors are the following: 
|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

We replace the above eigenvectors in 
T_{\Delta}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle=\Lambda_{m_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{\Delta}\rangle
&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}+1}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\\+&
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}+1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
after a change of summation indices we obtain
&\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}T_{0}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\\+&
\sum_{k_{2}=1}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{2}^{m_{2}+1}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\\+&
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=1}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}+\Delta_{3}^{m_{3}+1}\sum_{k_{2}=0}^{m_{2}}\Delta_{2}^{k_{2}}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\sum_{k_{2}=0}^{m_{2}}\sum_{k_{3}=0}^{m_{3}}\Delta_{2}^{k_{2}}\Delta_{3}^{k_{3}}\Lambda_{m_{1},m_{2}}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}.
We impose the powers of $\Delta_{2}\Delta_{3}$ to be equal. We obtain the following conditions 
\item $k_{2}=0$ and $k_{3}=0$
\begin{equation}\label{cond1}
	T_{0}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}=\Lambda_{m_{2},m_{3}}(x)G_{m_{2},m_{3},\epsilon}^{0,0}(x)|\Psi_{m_{1},m_{2}}^{0}\rangle|_{\epsilon=0}
\item $k_{2}=m_{2}+1$ and $k_{3}\in \{0,\ldots,m_{3}\}$
\begin{equation}\label{cond2}
		B_{2}(x)G_{m_{2},m_{3},\epsilon}^{m_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
\item $k_{2}\in\{0,\ldots,m_{2}\}$ and $k_{3}=m_{3}+1$
\begin{equation}\label{cond3}
		B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},m_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}=0
\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}\in\{1,\ldots,m_{3}\}$ 
\begin{equation}\label{cond4}
		&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}\left(B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+B_{3}(x)G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)\right)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\item $k_{2}=0$ and $k_{3}\in\{1,\ldots,m_{3}\}$
\begin{equation}\label{cond5}
		&	\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{2}(x)G_{m_{2},m_{3},\epsilon}^{k_{2}-1,0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
		=
		G_{m_{2},m_{3},\epsilon}^{k_{2},0}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
\item $k_{2}\in \{1,\ldots,m_{2}\}$ and $k_{3}=0$
\begin{equation}\label{cond6}
		&\left(\Lambda_{m_{2},m_{3}}(x)-T_{0}(x)\right)^{-1}B_{3}(x)G_{m_{2},m_{3},\epsilon}^{0,k_{3}-1}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}
		=
		G_{m_{2},m_{3},\epsilon}^{0,k_{3}}(x)|\Psi_{m_{2},m_{3}}^{0}\rangle|_{\epsilon=0}

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}

For the sake of notation we denote by 
\begin{equation}
\begin{split}
A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
\end{split}
\end{equation}
%{\color{red}Are we missing the prefactor $(N+2x)$?}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes

\begin{equation}\label{cond4A}
G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
We introduce the following indices
i_{1}=\ldots=i_{k_{2}}=2\qquad i_{k_{2}+1}=\ldots =i_{k_{2}+k_{3}}=3
Then, we introduce the permutation 
\sigma(i_{j})=i_{k}\qquad \forall j,k=1,\ldots,k_{2}+k_{3}
We write
G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
where we denoted by $\text{SYM}$ the symmetric group on $\{i_{1},\ldots,i_{k_{2}+k_{3}}\}$.\\
It solves \eqref{cond4A}, indeed
&A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
\\=&A_{2}\frac{k_{2}}{k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}\frac{k_{3}}{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
A_{2}\frac{k_{2}}{k_{2}}\frac{1}{(k_{2}-1)!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\\+&A_{3}\frac{k_{3}}{k_{3}}\frac{1}{k_{2}!(k_{3}-1)!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
\frac{1}{k_{2}!k_{3}!}\left(\sum_{\sigma \in \text{SYM}}k_{2}A_{2}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}+ \sum_{\sigma \in \text{SYM}}k_{3}A_{3}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\right)
\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
where in the up to last equality we used the fact that the quantity first summation is symmetric with respect to the exchange of $A_{2}$ and thus we have $k_{2}$ equal terms. Similarly, for the second summation using the symmetry with respect to $A_{3}$. \\
This argument can be generalized for $N>2$ species introducing
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\frac{1}{k_{2}!\cdots k_{N}!}\sum_{\sigma\in \text{SYM}}A_{i_{1}}\cdots A_{i_{k_{2}+\cdots+k_{N}}}
where we assumed 
i_{1}=\cdots=i_{k_{2}}=2,\qquad \ldots \qquad i_{k_{2}+\cdots+k_{N-1}}=\cdots=i_{k_{2}+\ldots+k_{N}}=N
To write its solution we define
\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group. \\
The following expression solves \eqref{cond4A}
G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).

@@

A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)

>>>>

\begin{equation}\label{S1-Whole}

@@

\begin{equation}\label{S2-Whole}

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory. Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz. This expression, as it will be show in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state. To write formula \eqref{W-extended} using the charges of the system, we the Quantum Inverse Scattering Method (QISM). We first present the simpler case of $gl(2)$, then we try to adapt the proof the general $gl(N)$. 

@@

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
\begin{equation}\label{B-charge}
		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

Since $Q^{2L}$ and $H$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with this more with this expression. Hopefully, using exchange relation between charges, we could try to handle \eqref{WInCharges} and rewrite it independently from the equilibrium eigenvectors. Moreover, we can use it to extract the steady state by rising the vacuum state. 

@@

Power expanding the matrix $W$ with respect to $\Delta=(\alpha-\beta)$ and

@@

We use the following series expansion

@@

\begin{equation}\label{Nice-W2}

@@

Following the result in the simpler $gl(2)$ case, we aim to generalize it to higher rank chains ($N>2$). Repeating the computations we find that 

@@

 Recalling the expression of $\mathcal{Q}^{2L}$ given in \eqref{Q-nonDiag} we write the multi-variable power expansion with respect to $\Delta_{i} B_{i}^{2L-1}$ for all $i\in\{1,\ldots,N-1\}$. We obtain that, using also the multi-variate version of \eqref{veryUsefulSeries},

@@

Here $SYM$ is the following transformation. We introduce, the following indices $i_{j}$ with $j=1,\ldots,k_{1}+\ldots+k_{N}$, such that 

@@

\begin{equation}\label{definitionA}

@@

&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\=&
SYM_{k_{1},\ldots,k_{N-1}}\left(A_{1},\ldots,A_{N-1}\right)\\
=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{1}+\ldots+k_{N-1}})}

@@

In this case, the commutation relations between $Q_{0}^{2L}$ and $B_{i}^{2L-1}$ are given by \eqref{ExQ0B-charges}. Exchanging $Q_{0}^{2L}$ with $B_{i}^{2L-1}$ generates also charges $B_{j}^{2L-1}$ with $j\neq 1$. Therefore, it is hard to obtain the multivariate equivalent of \eqref{Nice-W2}. 
\subsection{Non-equilibrium steady state from the W transformation}
By using $W$ it is possible to obtain all the non-equilibrium eigenvectors by the knowledge of the equilibrium ones. As a consequence, also the non-equilibrium steady state can by found by using $W$. For the $N=2$ chain, this property has been proved in \cite{frassek2020eigenstates}. Also for the $gl(N)$ case, we can retrieve the non-equilibrium steady state of the Hamiltonian $H^{''}$ given in \eqref{ResulsBasis}, by acting with $W$ on the vacuum state 
	|\Psi_{0}^{0}\rangle:=\underbrace{\begin{pmatrix}
		0\\
		0\\
		1
	\end{pmatrix}\otimes \cdots \otimes\begin{pmatrix}
		0\\
		0\\
		1
	\end{pmatrix}}_{L-\text{times}}
Therefore, we have that 
	|\Psi^{''}\rangle=W|\Psi_{0}^{0}\rangle
We do not write the full proof, but only the result for the first non-trivial case, i.e. a chain of length $L=2$ with $N=3$ species. We set $3$ as the empty species.  
\paragraph{Steady state for a $L=2$ and $N=3$ chain}
Here we have 
	|\Psi_{0}^{0}\rangle=\begin{pmatrix}
		0\\0\\1
	\end{pmatrix}\otimes \begin{pmatrix}
	0\\0\\1
\end{pmatrix}=|\phi_{33}\rangle
where we denoted by $(|\phi_{i}\rangle)_{j}=\delta_{j,i}$ the canonical basis of $\mathbb{C}^{3}$ and $|\phi_{ij}\rangle=|\phi_{i}\rangle\otimes|\phi_{j}\rangle$ the basis of the tensor product space $\mathbb{C}^{3}\otimes\mathbb{C}^{3}$. We have
|\Psi^{''}\rangle=&	W|\Psi_{0}^{0}\rangle =\lim_{\epsilon\to 0}\sum_{k_{1}=0}^{2}\sum_{k_{2}=0}^{2}\Delta_{1}^{k_{1}}\Delta_{2}^{k_{2}}2^{k_{1}+k_{2}}SYM_{k_{1},k_{2}}\left(A_{1},A_{2}\right)|\Psi_{0}^{0}\rangle
	\\=&\lim_{\epsilon\to 0}\left\{I+2\Delta_{1}A_{1}+2\Delta_{2}A_{2}+4\Delta_{1}^{2}A_{1}^{2}+4\Delta_{2}^{2}A_{2}^{2}+4\Delta_{1}\Delta_{2}\left(A_{1}A_{2}+A_{2}A_{1}\right)\right\}|\Psi_{0}^{0}\rangle
where we recall $A_{i}$ defined in \eqref{definitionA}. We need to compute the action of each addend in the last equality on the state $|\Psi_{0}^{0}\rangle$.\\
Using the charges computed in \eqref{B-charge} and \eqref{Q0Exp} we obtain that 
A_{i}=	&\left(\Lambda_{0}^{Q}+\epsilon-Q_{0}\right)^{-1}B_{i}^{2L-1}\\=&\left((28+\epsilon)I^{tot}-10e_{33}^{tot}-2(e_{11}^{tot}e_{11}^{tot}+e_{22}^{tot}e_{22}^{tot}+e_{33}e_{33}^{tot})-2(e_{12}^{tot}e_{21}^{tot}+e_{21}^{tot}e_{12}^{tot})\right)^{-1}\\&\left(2e_{i3}^{tot}+2e_{i3}^{tot}e_{33}-2(e_{ii}^{[1]}e_{i3}^{[b]}+e_{i2}^{[2]}e_{23}^{[1]})\right)
By the help of an algebraic manipulator we obtain 

@@

	\lim_{\epsilon\to 0}2\Delta_{1}A_{1}|\phi_{33}\rangle&=\frac{2}{3}\Delta_{1}|\phi_{13}\rangle+\frac{1}{3}\Delta_{1}|\phi_{31}\rangle\\
	\lim_{\epsilon\to 0}2\Delta_{2}A_{2}|\phi_{33}\rangle&=\frac{2}{3}\Delta_{2}|\phi_{23}\rangle+\frac{1}{3}\Delta_{3}|\phi_{32}\rangle\\
\lim_{\epsilon\to 0}	4\Delta_{1}^{2}A_{1}^{2}|\phi_{33}\rangle&=\frac{1}{6}\Delta_{1}^{2}|\phi_{11}\rangle\\
